---
title: "Part 6 (ch24)  Questions Numeric"
---

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p5num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p7num.qmd){.btn .btn-primary role="button" data-toggle="tool"}
:::


::: {.callout-note}
### For students

**Last updated: `r format(Sys.time(), '%d/%m/%Y')`  **

**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**

:::


___


## Q1

```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

face_value <- 1000
conversion_ratio <- rnorm(1, mean = 40, sd = 3)
conversion_price <- face_value / conversion_ratio
```

**Q**: You own a bond with a face value of $`r face_value` and a conversion ratio of `r round(conversion_ratio, 2)`.
What is the the conversion price? `r fitb( round(conversion_price, 0), tol = 1)`

**Answer**:

1) `r round(conversion_price, 2)`

___

## Q2
```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

face_value <- 1000
conversion_ratio <- rnorm(1, mean = 40, sd = 3)
conversion_price <- face_value / conversion_ratio

```

**Q**: You own a bond with a face value of $`r face_value` and a conversion price of $`r round(conversion_price, 2)`.
What is the the conversion ratio? `r fitb( round(conversion_ratio, 0), tol = 1)`

**Answer**:

1) `r round(conversion_ratio, 2)`



___


::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p5num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p7num.qmd){.btn .btn-primary role="button" data-toggle="tool"}
:::