---
title: Ibovespa vs. Ibovespa in dollar
description: |
  Graphing Ibovespa in dollar using ipeadatar.
categories:
  - Finance
  - Open Data
  - Open Code
author: Henrique C. Martins
date: 20/08/2022

---


Let's see how to create a graph of Ibovespa in dollar using data from ipeadata. Start by installing and loading the following package. 

```{r}
library(ipeadatar)
```    


Then, download the data. You will need the variables' codes. You can use the row below to see the codes of all variables available.

```{r}
all_series <- available_series()
```    


Then, after learning the codes for the variables we want (i.e., the codes 'GM366_IBVSP366' and 'GM366_ERC366' below), you download the data.   

```{r}
ibov  <- ipeadata(code = "GM366_IBVSP366")
dolar <- ipeadata(code = "GM366_ERC366")
```

    
See that the period available is different for the two variables.

For convenience, let's delete some columns in Ibov and integrate the dollar to Ibov. 

```{r}
ibov <-subset(ibov, select=-c(tcode,uname))
dolar<-subset(dolar, select=-c(tcode,uname))
```

The next step is to join the data by date to avoid using different periods in each dataframe.

```{r}
data <- merge(ibov,dolar, by = "date")
```


Then, let's calculate the ratio between Ibovespa and dollar each day.     

```{r}
data$ibov_dolar <- (data$value.x/data$value.y)
```
    
Lastly, you are good to go, and you can create a graph as follows.


```{r}
library(ggplot2)
library(ggthemes)
ggplot(data, aes(x = date, y=ibov_dolar) ) + geom_line(color='#377E14') +  
  labs(y='Ibov in USD', 
       title = "Graph of Ibov in USD (Period: since 1994)",
       caption = "Source: Ipeadata (R package: ipeadatar)") + theme_solarized()

```


This graph is simply a reminder of the value in dollar of our Stock market index. It shows that, at the moment, Ibovespa in dollar is not as high as one may think.


Below is a graph of Ibov in Euros.

```{r}
euro <- ipeadata(code = "GM366_EUROC366")
euro <-subset(euro, select=-c(tcode,uname))
data2 <- merge(ibov,euro, by = "date")
data2$ibov_euro <- (data2$value.x/data2$value.y)
ggplot(data2, aes(x = date, y=ibov_euro) ) + geom_line(color='#142E7E') +  
  labs(y='Ibov in USD', 
       title = "Graph of Ibov in Euro (Period: since 1999)",
       caption = "Source: Ipeadata (R package: ipeadatar)") + theme_solarized()

```


Thanks for passing by!



