---
title: "Part 1 (ch24) Questions Numeric"
---

::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::


## Question 1






```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
iinvest <- round(  0.05 +runif(1,0.001,0.01) , 3)
ishares1 <- 1
ishares2 <- 0.75
ishares3 <- 2
ainvest <- 3
share <- ainvest / ishares3
```

You founded your own firm two years ago. Initially, you contributed **`r iinvest` million**  of your money and, in return, received **`r round(ishares1,3)` million** shares of stock. Since then, you have sold an additional **`r round(ishares2,3)` million** shares to angel investors. You are now considering raising even more capital from a venture capitalist. The venture capitalist has agreed to invest **`r round(ainvest,3)` million**  and receive **`r round(ishares3,3)` million** shares. Assuming that this is the venture capitalist’s first investment in your company. 

**What is the post-money valuation, in million? ** `r fitb( round( (ishares1 + ishares2 + ishares3 ) * share ,3) , tol=0.001)`

**Assuming that this is the venture capitalist’s first investment in your company, what percentage of the firm will he or she end up owning?**  `r fitb( round( ishares3 / (ishares1 + ishares2 + ishares3 ) * 100 , 3) , tol=0.001)`

**What percentage will you own?**  `r fitb( round( ishares1 / (ishares1 + ishares2 + ishares3 ) * 100 , 3) , tol=0.001)`

**What is the value of your shares, in million?**  `r fitb( round( ishares1  * share ,3) , tol=0.001)`


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

seriesapre <- round( runif(1, 1,5) ,3 )
seriesapost <- round(seriesapre +  runif(1, 1,5),3 )

seriesbpre <- round(seriesapost + runif(1, 10,50),3 )
seriesbpost <- round(seriesbpre +  runif(1, 10,50),3 )

seriescpre <- round(seriesbpost + runif(1, 50,70),3 )
seriescpost <- round(seriescpre +  runif(1, 50,70),3 )

```




**Answers**:


1) `r round( (ishares1 + ishares2 + ishares3 ) * share ,3) `

2) `r round( ishares3 / (ishares1 + ishares2 + ishares3 ) * 100 , 3) `

3) `r round( ishares1 / (ishares1 + ishares2 + ishares3 ) * 100 , 3) `

4) `r round( ishares1  * share ,3) `



___



## Question 2



```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

seriesapre <- round( runif(1, 1,5) ,3 )
seriesapost <- round(seriesapre +  runif(1, 1,5),3 )

seriesbpre <- round(seriesapost + runif(1, 10,50),3 )
seriesbpost <- round(seriesbpre +  runif(1, 10,50),3 )

seriescpre <- round(seriesbpost + runif(1, 50,70),3 )
seriescpost <- round(seriescpre +  runif(1, 50,70),3 )



```



**Q:** A company has raised capital as follows (in millions USD). 

\item Series A Pre-Money: **`r  round( seriesapre ,3) `** & Series A Post-Money: **`r  round( seriesapost ,3) `**

\item Series B Pre-Money: **`r  round( seriesbpre ,3) `** & Series B Post-Money: **`r  round( seriesbpost ,3) `**

\item Series C Pre-Money: **`r  round( seriescpre ,3) `** & Series C Post-Money: **`r  round( seriescpost ,3) `**

**How much did the company raised in each round, in millions?**

Round A: `r fitb( round( (seriesapost - seriesapre )  ,3) , tol=0.001)`, Round B: `r fitb( round( (seriesbpost - seriesbpre ) ,3) , tol=0.001)`, Round C: `r fitb( round( (seriescpost - seriescpre )  ,3) , tol=0.001)`



**Assuming no other securities were issued, what fraction of the firm’s shares were held by common shareholders (founders and employees) after each round, in percent?**

Round A: `r fitb( round( 100*(seriesapre / seriesapost )  ,3) , tol=0.001)`, Round B: `r fitb( round( 100*(seriesbpre / seriesbpost * seriesapre / seriesapost ) ,3) , tol=0.001)` , Round C: `r fitb( round( 100*(seriescpre / seriescpost * seriesapre / seriesapost * seriesbpre / seriesbpost)  ,3) , tol=0.001)`













**Answers:**

1) 

Round A: `r round(seriesapost ,3)` -  `r round( seriesapre   ,3) `  = `r round( (seriesapost - seriesapre )  ,3) `

Round B: `r round(seriesbpost ,3)` -  `r round( seriesbpre   ,3) `  = `r round( (seriesbpost - seriesbpre ) ,3) ` 

Round C: `r round(seriescpost ,3)` -  `r round( seriescpre   ,3) `  =`r round( (seriescpost - seriescpre )  ,3) `

2) 

Round A: `r round(seriesapre ,3)` /  `r round( seriesapost   ,3) `  = `r round( 100*(seriesapre / seriesapost )  ,3) `

Round B: `r round(seriesbpre ,3)` /  `r round( seriesbpost   ,3) ` *   `r round( seriesapre   ,3)` /  `r round( seriesapost   ,3)` = `r round( 100*(seriesbpre / seriesbpost * seriesapre / seriesapost ) ,3) ` 

Round C: `r round(seriescpre ,3)` /  `r round( seriescpost   ,3) ` *   `r round( seriesapre   ,3)` /  `r round( seriesapost   ,3)` * `r round(seriesbpre ,3)` /  `r round( seriesbpost   ,3) ` = `r round( 100*(seriescpre / seriescpost * seriesapre / seriesapost * seriesbpre / seriesbpost)  ,3) `



___

