---
title: "Part 1 (ch23)  Questions T/F & Multiple Choice"
---


::: {style="text-align: right"}
[Go to next Chapter](p2tf.qmd){.btn .btn-primary .btn role="button" data-toggle="tool}
:::

::: {.callout-warning}
### For students

**Last updated: `r format(Sys.time(), '%d/%m/%Y')`  **

Below you find many questions to this chapter. 

*As this link is continuously updated with new questions, you might expect some changes from time to time.*

The Questions are based or inspired on either [**Berk & DeMarzo, Corporate Finance, 5th ed. 2020**](https://www.amazon.com.br/Corporate-Finance-Global-Jonathan-Berk/dp/1292304154) or 
[**Brealey & Myers, Principles of Corporate Finance, 13th ed. 2020**](https://www.amazon.com.br/Principles-Corporate-Finance-Richard-Brealey/dp/1260565556/ref=sr_1_3?refinements=p_27%3ABrealey+Myers&s=books&sr=1-3).

*If you are interest in getting a `.pdf` version of your answers, hit `Ctrl + P` to print*

:::


___

**Mark T (True) or F (False) in each of the following sentences.**





```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false


cat('
<div id="quiz-container">

  <p><strong>1.</strong> An underwriter is an investment bank that manages the IPO process and helps the company sell its stock.</p>
  <input type="text" id="q1" placeholder="T or F">
  <div class="feedback" id="f1" style="display:none; color: green;">✅ Correct: This is the definition of an underwriter.</div>

  <p><strong>2.</strong> An IPO is not necessarily the first time a company sells its stock to the public.</p>
  <input type="text" id="q2" placeholder="T or F">
  <div class="feedback" id="f2" style="display:none; color: red;">❌ Incorrect: An IPO <em>is</em> the first time shares are sold to the public.</div>

  <br><br>
  <button onclick="checkAnswers()" 
          style="background-color:#28a745; color:white; padding:10px 20px; border:none; border-radius:5px; cursor:pointer;">
    Check Answers
  </button>

  <p id="score" style="font-weight: bold;"></p>

</div>

<script>
function checkAnswers() {
  let correct = 0;

  // Q1
  const a1 = document.getElementById("q1").value.trim().toUpperCase();
  if (a1 === "T") {
    correct++;
    document.getElementById("f1").style.color = "green";
  } else {
    document.getElementById("f1").style.color = "red";
  }
  document.getElementById("f1").style.display = "block";

  // Q2
  const a2 = document.getElementById("q2").value.trim().toUpperCase();
  if (a2 === "F") {
    correct++;
    document.getElementById("f2").style.color = "green";
  } else {
    document.getElementById("f2").style.color = "red";
  }
  document.getElementById("f2").style.display = "block";

  document.getElementById("score").textContent = "You got " + correct + " out of 2 correct.";
}
</script>
')



```







___

**And here are some additional multiple choice problems.**


::: {.webex-check .webex-box}

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
q1 <- " **Q1: Which of the following issues have the expected highest total direct costs of issuing as a percentage of gross proceeds?**"
q1_choices <- c(answer="Initial public offerings (IPOs)",
                 "Seasoned equity offerings (SEOs)",
                 "Convertible bonds",
                 "Straight bonds")
cat(q1,longmcq(q1_choices))


q2 <- " **Q2: Which of the following factors is typically considered in determining the timing of an initial public offering (IPO)?**"
q2_choices <- c("Market conditions and investor sentiment",
                 "Firm's capital needs",
                 "Industry regulations and compliance requirements",
                 answer="All of the above")
cat(q2,longmcq(q2_choices))


```

:::





___

<script src="https://giscus.app/client.js"
        data-repo="henriquecastror/EF_permanent"
        data-repo-id="R_kgDOLMIejg"
        data-category="General"
        data-category-id="DIC_kwDOLMIejs4Cc1yS"
        data-mapping="number"
        data-term="1"
        data-reactions-enabled="1"
        data-emit-metadata="0"
        data-input-position="bottom"
        data-theme="light"
        data-lang="en"
        crossorigin="anonymous"
        async>
</script>



::: {style="text-align: right"}
[Go to next Chapter](p2tf.qmd){.btn .btn-primary .btn role="button" data-toggle="tool}
:::





cat("1", fitb("T", num = FALSE, ignore_case = TRUE), "An underwriter is an investment bank that manages the IPO process and helps the company sell its stock.", "\n\n")
cat("2", fitb("F", num = FALSE, ignore_case = TRUE), "An initial public offering (IPO) is not necessarily the first time a company sells its stock to the public.", "\n\n")
cat("3", fitb("F", num = FALSE, ignore_case = TRUE), "Underwriters face no risk during an IPO, so that a greenshoe provision is usually not necessary.", "\n\n")
cat("4", fitb("T", num = FALSE, ignore_case = TRUE), "New issues are highly cyclical.", "\n\n")
cat("5", fitb("F", num = FALSE, ignore_case = TRUE), "The transaction costs of an IPO are usually low.", "\n\n")
cat("6", fitb("T", num = FALSE, ignore_case = TRUE), "IPOs are underpriced on average.", "\n\n")
cat("7", fitb("T", num = FALSE, ignore_case = TRUE), "A seasoned equity offering (SEO) is the sale of stock by a company that is already publicly traded.", "\n\n")
cat("8", fitb("F", num = FALSE, ignore_case = TRUE), "A cash offer occurs when new shares are offered only to existing shareholders.", "\n\n")
cat("9", fitb("F", num = FALSE, ignore_case = TRUE), "A rights offer occurs when new shares are sold to investors at large.", "\n\n")
cat("10", fitb("F", num = FALSE, ignore_case = TRUE), "The stock price reaction to an SEO is positive on average.", "\n\n")
cat("11", fitb("T", num = FALSE, ignore_case = TRUE), "Bookbuilding is a common method used by underwriters to determine the IPO price.", "\n\n")
cat("12", fitb("F", num = FALSE, ignore_case = TRUE), "Investors in an IPO are guaranteed to receive shares at the offering price.", "\n\n")
cat("13", fitb("T", num = FALSE, ignore_case = TRUE), "Lock-up periods restrict company insiders from selling their shares immediately after an IPO.", "\n\n")
cat("14", fitb("T", num = FALSE, ignore_case = TRUE), "A roadshow is a series of presentations made by company executives to potential investors.", "\n\n")
cat("15", fitb("F", num = FALSE, ignore_case = TRUE), "In a greenshoe option, underwriters buy shares back from the market to stabilize the stock price.", "\n\n")
cat("16", fitb("T", num = FALSE, ignore_case = TRUE), "IPO allocation refers to the process of distributing shares to various investors.", "\n\n")
cat("17", fitb("F", num = FALSE, ignore_case = TRUE), "Quiet period is a term used to describe the period after an IPO when company executives cannot communicate with the public.", "\n\n")
cat("18", fitb("T", num = FALSE, ignore_case = TRUE), "The secondary market involves the trading of existing shares among investors.", "\n\n")
cat("19", fitb("T", num = FALSE, ignore_case = TRUE), "Market capitalization is a measure of a company's value, calculated by multiplying its stock price by the number of outstanding shares.", "\n\n")
cat("20", fitb("F", num = FALSE, ignore_case = TRUE), "The lock-up period for insiders typically lasts for a short duration, usually a week.", "\n\n")
cat("21", fitb("T", num = FALSE, ignore_case = TRUE), "Dilution occurs when a company issues additional shares, reducing the ownership percentage of existing shareholders.", "\n\n")
cat("22", fitb("F", num = FALSE, ignore_case = TRUE), "The primary market involves the buying and selling of existing shares among investors.", "\n\n")
cat("23", fitb("T", num = FALSE, ignore_case = TRUE), "Underwriters in an IPO often form a syndicate to share the responsibility of selling the new issue.", "\n\n")
cat("24", fitb("F", num = FALSE, ignore_case = TRUE), "The process of selling stock to the public for the first time is called a seasoned equity offering (SEO)", "\n\n")
cat("25", fitb("T", num = FALSE, ignore_case = TRUE), "Public companies typically have access to much larger amounts of capital through the public markets.", "\n\n")
cat("26", fitb("T", num = FALSE, ignore_case = TRUE), "By going public, companies give their private equity investors the ability to diversify.", "\n\n")
cat("27", fitb("T", num = FALSE, ignore_case = TRUE), "The two advantages of going public are greater liquidity and better access to capital.", "\n\n")
cat("28", fitb("T", num = FALSE, ignore_case = TRUE), "Before an IPO, the company prepares the final registration statement and final prospectus containing all the details of the IPO, including the number of shares offered and the offer price.", "\n\n")
cat("29", fitb("F", num = FALSE, ignore_case = TRUE), "A common practice of early investors in private companies is to stay for a long time, i.e., years after the company's IPO.", "\n\n")
cat("30", fitb("F", num = FALSE, ignore_case = TRUE), "Institutional investors, like big Banks, who buy equity in small private firms are called angel investors.", "\n\n")
cat("31", fitb("T", num = FALSE, ignore_case = TRUE), "A follow-on offering occurs when a publicly traded company issues additional shares after its IPO.", "\n\n")
cat("32", fitb("F", num = FALSE, ignore_case = TRUE), "An IPO always increases the wealth of existing shareholders.", "\n\n")
cat("33", fitb("T", num = FALSE, ignore_case = TRUE), "Investment banks play a crucial role in pricing and marketing new stock issues.", "\n\n")
cat("34", fitb("T", num = FALSE, ignore_case = TRUE), "The aftermarket performance of an IPO is often unpredictable and subject to market conditions (but many IPOs have a positive first-day return).", "\n\n")
cat("35", fitb("F", num = FALSE, ignore_case = TRUE), "A company must always conduct an IPO to raise equity capital.", "\n\n")
cat("36", fitb("T", num = FALSE, ignore_case = TRUE), "The Dutch auction method allows investors to bid for shares in an IPO, determining the final offer price.", "\n\n")
cat("37", fitb("T", num = FALSE, ignore_case = TRUE), "A dual-class share structure allows company founders to maintain control even after going public.", "\n\n")
cat("38", fitb("T", num = FALSE, ignore_case = TRUE), "Regulatory filings must be submitted before an IPO.", "\n\n")
cat("39", fitb("F", num = FALSE, ignore_case = TRUE), "IPOs eliminate financial risk for company founders and early investors.", "\n\n")
cat("40", fitb("T", num = FALSE, ignore_case = TRUE), "The CVM requires full disclosure of financials and risks in an IPO prospectus.", "\n\n")
cat("41", fitb("F", num = FALSE, ignore_case = TRUE), "The stock price of a newly public company is always stable in the first year post-IPO.", "\n\n")
cat("42", fitb("T", num = FALSE, ignore_case = TRUE), "Liquidity risk is one of the major concerns for investors in newly public companies.", "\n\n")