---
title: "Part 1 (ch24) Questions Numeric"
---

::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::


## Question 1



```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
p1 <- rnorm(1, mean = 10, sd = 2)
p2 <- rnorm(1, mean = 10, sd = 2)
div <- rnorm(1, mean = 1, sd = 0.1)
```

**Q:** You bought a stock one year ago for `r round(p1,3)` per share and sold it today for `r round(p2,3)`. It paid a `r round(div,3)` per share dividend today.

What was your realized return?

`r fitb( round( (p2-p1+div)/p1 * 100 ,3) , tol=0.001)`

How much of the return came from dividend yield and how much came from capital gain?

- Dividend Yield: `r fitb(round( (div)/p1 * 100 ,3) , tol=0.001)`

- Capital gain: `r fitb(round( (p2-p1)/p1 * 100 ,3) , tol=0.001)`

___

**Answer**:

1) `r  round( (p2-p1+div)/p1 * 100 ,3) `

2) `r round( (div)/p1 * 100 ,3) `

3) `r round( (p2-p1)/p1 * 100 ,3) `



___



## Question 2


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
mrp <- rnorm(1, mean = 8, sd = 0.01)
rf <- rnorm(1, mean = 5, sd = 0.01)
beta <- rnorm(1, mean = 0.9, sd = 0.2)
```

**Q:** Suppose the market risk premium is `r round(mrp,3)` and the risk-free interest rate is `r round(rf,3)`. Calculate the cost of capital of investing in a project with a beta of `r round(beta,3)`? 

`r fitb( round(rf + beta * mrp ,3) , tol=0.001)`

___

**Answer**:

1) `r round(rf + beta * mrp ,3) `


___


<script src="https://giscus.app/client.js"
        data-repo="henriquecastror/EF_permanent"
        data-repo-id="R_kgDOLMIejg"
        data-category="General"
        data-category-id="DIC_kwDOLMIejs4Cc1yS"
        data-mapping="number"
        data-term="4"
        data-reactions-enabled="1"
        data-emit-metadata="0"
        data-input-position="bottom"
        data-theme="light"
        data-lang="en"
        crossorigin="anonymous"
        async>
</script>
