---
title: "Part 2 (ch10) Questions Numeric"
---


::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p1num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p3num.qmd){.btn .btn-primary role="button" data-toggle="tool"}
:::

::: {.callout-note}
### For students

**Last updated: `r format(Sys.time(), '%d/%m/%Y')`  **

**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**

:::



## Question 1

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
p1 <- rnorm(1, mean = 10, sd = 2)
p2 <- rnorm(1, mean = 10, sd = 2)
div <- rnorm(1, mean = 1, sd = 0.1)
```

**Q:** You bought a stock one year ago for `r round(p1,3)` per share and sold it today for `r round(p2,3)`. It paid a `r round(div,3)` per share dividend today.

What was your realized return? `r fitb( round( (p2-p1+div)/p1 * 100 ,3) , tol=0.001)`

How much of the return came from dividend yield and how much came from capital gain?

- Dividend Yield: `r fitb(round( (div)/p1 * 100 ,3) , tol=0.001)`

- Capital gain: `r fitb(round( (p2-p1)/p1 * 100 ,3) , tol=0.001)`


**Answer**:

**1)** `r  round( (p2-p1+div)/p1 * 100 ,3)`. **2)** `r round( (div)/p1 * 100 ,3)`. **3)** `r round( (p2-p1)/p1 * 100 ,3) `



___



## Question 2


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
mrp <- rnorm(1, mean = 8, sd = 0.01)
rf <- rnorm(1, mean = 5, sd = 0.01)
beta <- rnorm(1, mean = 0.9, sd = 0.2)
```

**Q:** Suppose the market risk premium is `r round(mrp,3)` and the risk-free interest rate is `r round(rf,3)`. Calculate the cost of capital of investing in a project with a beta of `r round(beta,3)`? `r fitb( round(rf + beta * mrp ,3) , tol=0.001)`


**Answer**:

**1)** `r round(rf + beta * mrp ,3) `


___


## Question 3

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
p_buy <- rnorm(1, mean = 50, sd = 5)
p_sell <- rnorm(1, mean = 55, sd = 5)
div_yield <- rnorm(1, mean = 2, sd = 0.5)
```


Q: You bought a stock for `r round(p_buy,2)` per share and sold it later for `r round(p_sell,2)`. It paid `r round(div_yield,2)` in dividends over the period.

What was your holding period return in percentage terms? `r fitb( round( (p_sell - p_buy + div_yield) / p_buy * 100 ,2) , tol=0.01)`


**Answer**:

**1)** `r round( (p_sell - p_buy + div_yield) / p_buy * 100 ,2)` 



___



## Question 4


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
p1 <- rnorm(1, mean = 100, sd = 10)
p2 <- rnorm(1, mean = 130, sd = 10)
div <- rnorm(1, mean = 3, sd = 1)
years <- sample(1:5, 1)
```

Q: You bought a stock for `r round(p1,2)` per share and sold it for `r round(p2,2)` after `r years` years. You received `r round(div,2)` in dividends per year.

What was your total return over the period? `r fitb( round( (p2 - p1 + div * years) / p1 * 100 ,2) , tol=0.01)`

What was your annualized return (CAGR)? `r fitb( round(( ((p2 + div * years) / p1)^(1/years) - 1 )* 100 ,2) , tol=0.01)`


**Answer**:

**1)** `r  round( (p2 - p1 + div * years) / p1 * 100 ,2) `.  **2)** `r round(  (((p2 + div * years) / p1)^(1/years) - 1 ) * 100, 2  ) `



___

## Question 5

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
returns <- rnorm(5, mean = 8, sd = 3)
std_dev <- sd(returns)
```

Q: The past five annual returns of a stock were (in %): `r round(returns, 2)`

What was the average return? `r fitb(round(mean(returns),2), tol=0.01)`

What was the standard deviation of the returns? `r fitb(round(std_dev,2), tol=0.01)`



**Answer**:

**1)** `r round(  mean(returns) , 2 )`.  **2)** `r (round(std_dev,2))`


___


<script src="https://giscus.app/client.js"
        data-repo="henriquecastror/EF_permanent"
        data-repo-id="R_kgDOLMIejg"
        data-category="General"
        data-category-id="DIC_kwDOLMIejs4Cc1yS"
        data-mapping="number"
        data-term="4"
        data-reactions-enabled="1"
        data-emit-metadata="0"
        data-input-position="bottom"
        data-theme="light"
        data-lang="en"
        crossorigin="anonymous"
        async>
</script>

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p1num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p3num.qmd){.btn .btn-primary role="button" data-toggle="tool"}
:::