---
title: "Part 3 (ch11)  Questions T/F & Multiple Choice"

---

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p2tf.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p4tf.qmd){.btn .btn-primary role="button" data-toggle="tool"}
:::


::: {.callout-warning}
### For students

**Last updated: `r format(Sys.time(), '%d/%m/%Y')`  **

Below you find many questions to this chapter. 

*As this link is continuously updated with new questions, you might expect some changes from time to time.*

The Questions are based or inspired on either [**Berk & DeMarzo, Corporate Finance, 5th ed. 2020**](https://www.amazon.com.br/Corporate-Finance-Global-Jonathan-Berk/dp/1292304154) or 
[**Brealey & Myers, Principles of Corporate Finance, 13th ed. 2020**](https://www.amazon.com.br/Principles-Corporate-Finance-Richard-Brealey/dp/1260565556/ref=sr_1_3?refinements=p_27%3ABrealey+Myers&s=books&sr=1-3).

*If you are interest in getting a `.pdf` version of your answers, hit `Ctrl + P` to print*

:::

___


**Mark T (True) or F (False) in each of the following sentences.**



::: {.webex-check .webex-box}

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)

cat("1", fitb("F", num = FALSE, ignore_case = TRUE), "Buying shares of security *i* improves the Sharpe ratio of a portfolio if its expected return does not exceed the required return.", "\n\n")
cat("2", fitb("F", num = FALSE, ignore_case = TRUE), "The expected variance of a portfolio is the weighted average of the expected variances of the investments within it, using the portfolio weights.", "\n\n")
cat("3", fitb("T", num = FALSE, ignore_case = TRUE), "Diversification eliminates independent risks. The volatility of a large portfolio results from the common risk between the stocks in the portfolio." , "\n\n")
cat("4", fitb("T", num = FALSE, ignore_case = TRUE), "Short selling extends the set of possible portfolios.", "\n\n")
cat("5", fitb("F", num = FALSE, ignore_case = TRUE), "Investors mainly worry about those risks that can be eliminated through diversification.", "\n\n")
cat("6", fitb("T", num = FALSE, ignore_case = TRUE), "Efficient portfolios offer investors the highest possible expected return for a given level of risk.", "\n\n")
cat("7", fitb("T", num = FALSE, ignore_case = TRUE), "To find the risk of a portfolio, we need to know the degree to which stock returns move together. Covariance and correlation measure the co-movement of returns.", "\n\n")
cat("8", fitb("T", num = FALSE, ignore_case = TRUE), "The goal of an investor who is seeking to earn the highest possible expected return for any level  of volatility is to find the portfolio that generates the steepest possible line when combined with the risk-free investment.", "\n\n")
cat("9", fitb("T", num = FALSE, ignore_case = TRUE), "Under the CAPM assumptions, the capital market line (CML), which is the set of portfolios obtained by combining the risk-free security and the market portfolio, is the set of portfolios with the highest possible expected return for any level of volatility.", "\n\n")
cat("10", fitb("T", num = FALSE, ignore_case = TRUE), "The variance of a portfolio depends on the covariance of the stocks within it.",  "\n\n")
cat("11", fitb("T", num = FALSE, ignore_case = TRUE), "Portfolios that offer the highest expected return for a given variance (or standard deviation) are known as efficient portfolios.",  "\n\n")
cat("12", fitb("F", num = FALSE, ignore_case = TRUE), "Investors mainly worry about those risks that can be eliminated through diversification.", "\n\n")
cat("13", fitb("T", num = FALSE, ignore_case = TRUE), "The market portfolio is a tangency portfolio according to the CAPM.", "\n\n")
cat("14", fitb("T", num = FALSE, ignore_case = TRUE), "Beta measures the sensitivity of a stock's returns to the overall market movements.", "\n\n")
cat("15", fitb("T", num = FALSE, ignore_case = TRUE), "The efficient frontier represents the set of portfolios that offer the highest expected return for a given level of risk.", "\n\n")
cat("16", fitb("T", num = FALSE, ignore_case = TRUE), "The Sharpe ratio is a measure of risk-adjusted return, calculated by dividing the excess return of an investment by its standard deviation.", "\n\n")
cat("17", fitb("F", num = FALSE, ignore_case = TRUE), "The Security Market Line (SML) illustrates the relationship between expected return and systematic risk for individual securities, according to the Capital Asset Pricing Model (CAPM).", "\n\n")
cat("18", fitb("F", num = FALSE, ignore_case = TRUE), "A well-diversified portfolio always consists of assets with low or negative correlations to each other to reduce overall portfolio risk.", "\n\n")
cat("19", fitb("T", num = FALSE, ignore_case = TRUE), "The Markowitz Efficient Set refers to the collection of portfolios that offer the maximum expected return for any given level of portfolio risk, based on Harry Markowitz's Modern Portfolio Theory.", "\n\n")
cat("20", fitb("F", num = FALSE, ignore_case = TRUE), "An asset's standard deviation represents its systematic risk in the context of the Capital Asset Pricing Model (CAPM).", "\n\n")
cat("21", fitb("F", num = FALSE, ignore_case = TRUE), "An efficient portfolio has no risk at all.", "\n\n") 
cat("22", fitb("T", num = FALSE, ignore_case = TRUE), "The presence of a risk-free asset enables the investor to borrow or lend at the risk-free rate and form portfolios having greater Sharpe ratios.", "\n\n")
cat("23", fitb("F", num = FALSE, ignore_case = TRUE), "The security market line (SML) is the graph of expected rate of return on investment vs. the variance of returns.", "\n\n")
cat("24", fitb("F", num = FALSE, ignore_case = TRUE), "If a stock is overpriced, it would plot above the security market line.", "\n\n")
cat("25", fitb("T", num = FALSE, ignore_case = TRUE), "A stock's alpha is the difference between the expected return and the required return according to the CAPM.", "\n\n")
cat("26", fitb("T", num = FALSE, ignore_case = TRUE), "Beta measures the marginal contribution of a stock to the risk of a well-diversified portfolio.", "\n\n")
cat("27", fitb("F", num = FALSE, ignore_case = TRUE), "In equilibrium, it is possible to earn a return that is above the efficient frontier without the existence of a risk-free asset or some other asset that is uncorrelated with your portfolio assets.", "\n\n")
cat("28", fitb("T", num = FALSE, ignore_case = TRUE), "The Sharpe ratio measures the excess return per unit of risk.", "\n\n")
cat("29", fitb("T", num = FALSE, ignore_case = TRUE), "A stock's alpha reflects its performance relative to a benchmark index after adjusting for market risk.", "\n\n")
cat("29", fitb("T", num = FALSE, ignore_case = TRUE), "A stock with a beta of 0 is expected to have no correlation with market movements.", "\n\n")

```

:::





___

**And here are some additional multiple choice problems.**


::: {.webex-check .webex-box}

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
q1 <- " **Q1: How can an investor earn more than the return generated by the tangency portfolio and still stay on the security market line?**"
q1_choices <- c("Add high risk/return assets to the portfolio.",
                answer= "Borrow at the risk-free rate and invest in the tangency portfolio.",
                "Adjust the weight of stock in the portfolio to include fewer high-return stocks.",
                "It cannot be done.")
cat(q1,longmcq(q1_choices))

```

:::






___

<script src="https://giscus.app/client.js"
        data-repo="henriquecastror/EF_permanent"
        data-repo-id="R_kgDOLMIejg"
        data-category="General"
        data-category-id="DIC_kwDOLMIejs4Cc1yS"
        data-mapping="number"
        data-term="5"
        data-reactions-enabled="1"
        data-emit-metadata="0"
        data-input-position="bottom"
        data-theme="light"
        data-lang="en"
        crossorigin="anonymous"
        async>
</script>

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p2tf.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p4tf.qmd){.btn .btn-primary role="button" data-toggle="tool"}
:::