---
title: "Part 4 (ch12) Questions Numeric"
---

::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::


## Question 1


```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

```

### Cost of Equity Capital

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
mrp <- rnorm(1, mean = 8, sd = 0.01)
rf <- rnorm(1, mean = 5, sd = 0.01)
beta <- rnorm(1, mean = 1, sd = 0.2)
em <- mrp + rf
```

**Q:** Suppose a security's beta is `r round(beta,3)`. If the risk-free rate is `r round(rf,3)` percent and the market risk premium is `r round(mrp,3)` percent, calculate the security's cost of equity capital? 

`r fitb( round(rf + (beta * mrp) ,3), tol=0.01)`

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
mrp2 <- rnorm(1, mean = 8, sd = 0.01)
rf2 <- rnorm(1, mean = 5, sd = 0.01)
beta2 <- rnorm(1, mean = 1, sd = 0.2)
em2 <- mrp + rf
```

**Q:** Suppose a security's beta is `r round(beta2,3)`. If the risk-free rate is `r round(rf2,3)` percent and the expected return of the market portfolio is `r round(em2,3)` percent, calculate the security's cost of equity capital? 

`r fitb( round(rf2 + beta2 * (em2 - rf2 ) ,3) , tol=0.01)`

___


**Answer**:

1) `r round(rf + (beta * mrp) ,3)`

2) `r round(rf2 + beta2 * (em2 - rf2 ) ,3)`





## Question 2


### Cost of Debt 

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
rf <- rnorm(1, mean = 6.5, sd = 0.01)
yield <- rnorm(1, mean = 10, sd = 0.01)
mrp <- rnorm(1, mean = 8, sd = 0.01)
loss<- rnorm(1, mean = 7, sd = 0.01)
default <- rnorm(1, mean = 50, sd = 0.01)
beta <- 0.15
```

**Q:** Suppose a company has outstanding bonds with a yield to maturity of `r round(yield,3)` percent, a beta of `r round(beta,3)`, a rating with a probability of default of `r round(default,3)` percent and expected loss rate of `r round(loss,3)` percent. If corresponding risk-free rates were `r round(rf,3)` percent, and the market risk premium was `r round(mrp,3)` percent, estimate the expected return of the company's debt using the CAPM and the default rate method.

CAPM: `r fitb( round(rf + beta * mrp ,3), tol=0.01)`

Expected default method: `r fitb( round(yield - default/100 * loss   ,3), tol=0.01)`

___



**Answer**:

CAPM: `r round(rf + beta * mrp ,3)`

Expected default method: `r round(yield - default/100 * loss   ,3)`










___


<script src="https://giscus.app/client.js"
        data-repo="henriquecastror/EF_permanent"
        data-repo-id="R_kgDOLMIejg"
        data-category="General"
        data-category-id="DIC_kwDOLMIejs4Cc1yS"
        data-mapping="number"
        data-term="8"
        data-reactions-enabled="1"
        data-emit-metadata="0"
        data-input-position="bottom"
        data-theme="light"
        data-lang="en"
        crossorigin="anonymous"
        async>
</script>
