---
title: "Part 4 (ch12) Questions T/F & Multiple Choice"
---

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p3tf.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p5tf.qmd){.btn .btn-primary role="button" data-toggle="tool"}
:::

::: {.callout-warning}
### For students

**Last updated: `r format(Sys.time(), '%d/%m/%Y')`  **


Below you find many questions to this chapter. 

*As this link is continuously updated with new questions, you might expect some changes from time to time.*

The Questions are based or inspired on either [**Berk & DeMarzo, Corporate Finance, 5th ed. 2020**](https://www.amazon.com.br/Corporate-Finance-Global-Jonathan-Berk/dp/1292304154) or 
[**Brealey & Myers, Principles of Corporate Finance, 13th ed. 2020**](https://www.amazon.com.br/Principles-Corporate-Finance-Richard-Brealey/dp/1260565556/ref=sr_1_3?refinements=p_27%3ABrealey+Myers&s=books&sr=1-3).

*If you are interest in getting a `.pdf` version of your answers, hit `Ctrl + P` to print*

:::

___

**Mark T (True) or F (False) in each of the following sentences.**

::: {.webex-check .webex-box}

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)

cat("1", fitb("F", num = FALSE, ignore_case = TRUE), "A value-weighted portfolio is an equal-ownership portfolio.", "\n\n")
cat("2", fitb("T", num = FALSE, ignore_case = TRUE), "We can estimate a project’s cost of capital based on the asset or unlevered cost of capital of comparable firms in the same line of business.", "\n\n")
cat("3", fitb("T", num = FALSE, ignore_case = TRUE), "Because of default risk, the debt cost of capital, which is its expected return to investors, is less than its yield to maturity, which is its promised return.", "\n\n")
cat("4", fitb("F", num = FALSE, ignore_case = TRUE), "Because cash holdings will reduce a firm’s equity beta, when unlevering betas we can use the firm’s net debt, which is debt plus excess cash.", "\n\n")
cat("5", fitb("T", num = FALSE, ignore_case = TRUE), "The market portfolio is a value-weighted portfolio of all securities traded in the market. According to the CAPM, the market portfolio is efficient.", "\n\n")
cat("6", fitb("F", num = FALSE, ignore_case = TRUE), "If we regress a stock’s excess returns against the market’s excess returns, the intercept is the stock’s beta.", "\n\n")
cat("7", fitb("T", num = FALSE, ignore_case = TRUE), "To implement the CAPM, we must (a) construct the market portfolio, and determine its expected excess return over the risk-free interest rate, and (b) estimate the stock’s beta, or sensitivity to the market portfolio.", "\n\n")
cat("8", fitb("F", num = FALSE, ignore_case = TRUE), "Beta corresponds to the slope of the best fitting line in the plot of a security’s excess returns versus the market’s standard deviation.", "\n\n")
cat("9", fitb("T", num = FALSE, ignore_case = TRUE), "Firm or industry asset betas reflect the market risk of the average project in that firm or industry while individual projects may be more or less sensitive to the overall market.", "\n\n")
cat("10", fitb("T", num = FALSE, ignore_case = TRUE), "The weighted average cost of capital (WACC) is the discount rate used in capital budgeting to calculate the present value of cash flows arising from a project.", "\n\n")
cat("11", fitb("T", num = FALSE, ignore_case = TRUE), "An increase in a project’s systematic risk will lead to an increase in its required rate of return according to the CAPM.", "\n\n")
cat("12", fitb("F", num = FALSE, ignore_case = TRUE), "A firm's beta is independent of its capital structure.", "\n\n")
cat("13", fitb("T", num = FALSE, ignore_case = TRUE), "The cost of debt is the effective rate that a company pays on its borrowed funds, including interest and other fees.", "\n\n")
cat("14", fitb("F", num = FALSE, ignore_case = TRUE), "The cost of debt is always higher than the cost of equity for a company.", "\n\n")
cat("15", fitb("T", num = FALSE, ignore_case = TRUE), "The cost of debt can be calculated using the yield to maturity (YTM) on the company's existing debt.", "\n\n")
cat("16", fitb("F", num = FALSE, ignore_case = TRUE), "The cost of debt is the same for all companies within the same industry regardless of their financial health or creditworthiness.", "\n\n")
cat("17", fitb("T", num = FALSE, ignore_case = TRUE), "The cost of equity is the return required by equity investors for their investment in a company.", "\n\n")
cat("18", fitb("F", num = FALSE, ignore_case = TRUE), "The cost of equity is solely determined by the company's dividend yield and growth rate.", "\n\n")
cat("19", fitb("T", num = FALSE, ignore_case = TRUE), "The cost of debt can be calculated using the yield to maturity (YTM) of the firm’s outstanding bonds.", "\n\n")
cat("20", fitb("F", num = FALSE, ignore_case = TRUE), "The cost of debt and the interest rate on new loans are always the same.", "\n\n")
cat("21", fitb("T", num = FALSE, ignore_case = TRUE), "When calculating the cost of debt, we must adjust for taxes because interest expenses are tax-deductible.", "\n\n")
cat(22, fitb("F", num = FALSE, ignore_case = TRUE), "The cost of equity is always lower than the cost of debt because equity holders have a residual claim on assets.", "\n\n")
cat("23", fitb("T", num = FALSE, ignore_case = TRUE), "The Capital Asset Pricing Model (CAPM) is a common method used to estimate the cost of equity.", "\n\n")
cat("24", fitb("F", num = FALSE, ignore_case = TRUE), "The risk-free rate in the CAPM is usually the expected return of the stock market.", "\n\n")
cat("25", fitb("T", num = FALSE, ignore_case = TRUE), "Beta measures the systematic risk of a stock relative to the overall market.", "\n\n")
cat("26", fitb("T", num = FALSE, ignore_case = TRUE), "The equity risk premium (ERP) is the additional return investors require for holding risky stocks over risk-free securities.", "\n\n")
cat("27", fitb("F", num = FALSE, ignore_case = TRUE), "A company's historical return on equity (ROE) is the best estimate of its cost of equity.", "\n\n")
cat("28", fitb("T", num = FALSE, ignore_case = TRUE), "The weighted average cost of capital (WACC) incorporates both the cost of debt and the cost of equity.", "\n\n")
cat("29", fitb("F", num = FALSE, ignore_case = TRUE), "If a company has no debt, its WACC is equal to its cost of debt.", "\n\n")
cat("30", fitb("T", num = FALSE, ignore_case = TRUE), "The cost of debt should reflect the current market rate at which the company can issue new debt.", "\n\n")
cat("31", fitb("F", num = FALSE, ignore_case = TRUE), "Companies should always use book values instead of market values when calculating WACC.", "\n\n")
cat("32", fitb("T", num = FALSE, ignore_case = TRUE), "The yield to maturity (YTM) of a bond represents the annualized return an investor will earn if they hold the bond until maturity.", "\n\n")
cat("33", fitb("T", num = FALSE, ignore_case = TRUE), "If the risk-free rate increases, the cost of equity calculated using the CAPM will also increase.", "\n\n")
cat("34", fitb("T", num = FALSE, ignore_case = TRUE), "A decrease in a firm’s beta will generally lower its cost of equity according to the CAPM.", "\n\n")
cat("35", fitb("F", num = FALSE, ignore_case = TRUE), "Companies with a high beta have a lower cost of equity under the CAPM model.", "\n\n")
cat("36", fitb("F", num = FALSE, ignore_case = TRUE), "The cost of debt is not affected by changes in market interest rates.", "\n\n")
cat("37", fitb("T", num = FALSE, ignore_case = TRUE), "The risk-free rate used in the CAPM is often based on long-term government bond yields.", "\n\n")

cat("38", fitb("T", num = FALSE, ignore_case = TRUE), "The weighted average cost of capital (WACC) reflects the required return on the firm’s total capital.", "\n\n")
cat("39", fitb("T", num = FALSE, ignore_case = TRUE), "WACC can be used as the discount rate for evaluating new investment projects if the project has similar risk to the firm’s overall business.", "\n\n")
cat("40", fitb("F", num = FALSE, ignore_case = TRUE), "A company’s cost of capital is independent of market conditions.", "\n\n")
cat("41", fitb("T", num = FALSE, ignore_case = TRUE), "For firms with no publicly traded stock, the cost of equity can be estimated using industry betas and comparable firms.", "\n\n")
cat("42", fitb("T", num = FALSE, ignore_case = TRUE), "Asset beta measures the systematic risk of a firm’s assets and is independent of the firm’s capital structure.", "\n\n")
cat("43", fitb("F", num = FALSE, ignore_case = TRUE), "Debt beta is always zero because debt holders do not bear systematic risk.", "\n\n")
cat("44", fitb("T", num = FALSE, ignore_case = TRUE), "A firm’s equity beta is generally higher than its asset beta due to financial leverage.", "\n\n")
cat("45", fitb("F", num = FALSE, ignore_case = TRUE), "The asset beta of a leveraged firm is higher than the asset beta of an identical unleveraged firm.", "\n\n")


```

:::


___

**And here are some additional multiple choice problems.**


::: {.webex-check .webex-box}

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
q1 <- " **Q1: What is the relationship between a firm's cost of capital and its risk?**"
q1_choices <- c("Firms with higher risk have lower cost of capital.",
                answer= "Firms with lower risk have lower cost of capital.",
                 "There is no relationship between a firm's risk and its cost of capital.")
cat(q1,longmcq(q1_choices))


q2 <- " **Q2: If a firm uses the firm's cost of capital for evaluating all projects, which situation(s) will likely occur?** 1) The firm will accept poor low-risk projects. 2) The firm will reject good high-risk projects. 3) The firm will correctly accept projects with average risk."
q2_choices <- c("1 only",
                "2 only",
                "3 only",
                answer="1, 2, and 3")
cat(q2,longmcq(q2_choices))

```

:::




___

<script src="https://giscus.app/client.js"
        data-repo="henriquecastror/EF_permanent"
        data-repo-id="R_kgDOLMIejg"
        data-category="General"
        data-category-id="DIC_kwDOLMIejs4Cc1yS"
        data-mapping="number"
        data-term="7"
        data-reactions-enabled="1"
        data-emit-metadata="0"
        data-input-position="bottom"
        data-theme="light"
        data-lang="en"
        crossorigin="anonymous"
        async>
</script>

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p3tf.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p5tf.qmd){.btn .btn-primary role="button" data-toggle="tool"}
:::
