---
title: "Part 5 (ch13) Questions Numeric"
---

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p4num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
:::


::: {.callout-note}
### For students

**Last updated: `r format(Sys.time(), '%d/%m/%Y')`  **

**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**

:::


___


## Q1:  Alpha Calculation

```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

er <- rnorm(1, mean = 11, sd = 0.01)
mrp <- rnorm(1, mean = 7, sd = 0.01)
rf <- rnorm(1, mean = 3, sd = 0.01)
beta <- rnorm(1, mean = 1, sd = 0.2)
em <- mrp + rf

```



**Q**: Consider a stock whose expected return is  `r round(er,3)` and beta is  `r round(beta,3)`. The market risk premium is currently  `r round(mrp,3)`% and the return of the risk-free asset is  `r round(rf,3)`. What is the alpha of the stock?

`r fitb( round(   er - (rf+beta*mrp)      ,3) , tol=0.01)`



**Answer**:

1) `r round(er - (rf+beta*mrp)    ,3)`


___


## Q2:  Fama-French Portfolio 


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

r1 <- rnorm(1, mean = 5, sd = 0.01)
r2 <- rnorm(1, mean = 3, sd = 0.01)
r3 <- rnorm(1, mean = 4, sd = 0.01)
r4 <- rnorm(1, mean = 2.5, sd = 0.01)

b1a <- rnorm(1, mean = 0.9, sd = 0.01)
b2a <- rnorm(1, mean = 0.8, sd = 0.01)
b3a <- rnorm(1, mean = 0.7, sd = 0.01)
b4a <- rnorm(1, mean = 0.6, sd = 0.01)

b1b <- rnorm(1, mean = 1.0, sd = 0.02)
b2b <- rnorm(1, mean = 1.1, sd = 0.02)
b3b <- rnorm(1, mean = 1.2, sd = 0.02)
b4b <- rnorm(1, mean = 1.3, sd = 0.02)


```

**Q2:** Consider the following information regarding the Fama-French-Carhart four factor model. What is the expected return of Stock A (in %)? And Stock B (in %)? 

| Factor Port. | Average  Return (%) | Stock A  Betas | Stock B   Betas | 
|------------------|---------------------------|------------------|-----------------|
| Rm - rf          | `r round(r1,3)`              | `r round(b1a,3)`     | `r round(b1b,3)`       |
| SMB              | `r round(r2,3)`              | `r round(b2a,3)`     | `r round(b2b,3)`       |
| HML              | `r round(r3,3)`              | `r round(b3a,3)`     | `r round(b3b,3)`       |
| Mom.             | `r round(r4,3)`              | `r round(b4a,3)`     | `r round(b4b,3)`       | 


**Stock A:** `r fitb( round(  r1*b1a + r2*b2a +  r3*b3a+   r4*b4a      , 3) , tol=0.01)`

**Stock B:** `r fitb( round(  r1*b1b + r2*b2b +  r3*b3b+   r4*b4b      , 3) , tol=0.01)`


**Answer**:

A) `r round(r1*b1a + r2*b2a +  r3*b3a+   r4*b4a     ,3)`

B) `r round(r1*b1b + r2*b2b +  r3*b3b+   r4*b4b     ,3)`








___


<script src="https://giscus.app/client.js"
        data-repo="henriquecastror/EF_permanent"
        data-repo-id="R_kgDOLMIejg"
        data-category="General"
        data-category-id="DIC_kwDOLMIejs4Cc1yS"
        data-mapping="number"
        data-term="11"
        data-reactions-enabled="1"
        data-emit-metadata="0"
        data-input-position="bottom"
        data-theme="light"
        data-lang="en"
        crossorigin="anonymous"
        async>
</script>


::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p4num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
:::