---
title: "Part 7 (ch14)  Questions Numeric"
---

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p6num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
:::


::: {.callout-note}
### For students

**Last updated: `r format(Sys.time(), '%d/%m/%Y')`  **

**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**

:::

___


## Q1

```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

# Given data
value_strong <- rnorm(1, mean = 600, sd = 3)
value_weak <- rnorm(1, mean = 300, sd = 3)
prob_strong <- 0.5
prob_weak <- 0.5
market_value_today <- rnorm(1, mean = 400, sd = 3)

expected_future_value <- prob_strong * value_strong + prob_weak * value_weak
expected_return <- (expected_future_value - market_value_today) / market_value_today * 100


```


**Q**: Company X has no debt. Its assets will be worth `r round(value_strong, 1)` million in one year if the economy is strong, but only `r round(value_weak, 1)` million if the economy is weak. Both events are equally likely. The market value today of X's assets is `r round(market_value_today, 1)` million. What is the expected return without leverage (in %)? `r fitb(round(expected_return, 1), tol = 0.5)`

**Answer:** `r round(expected_return, 2)` %

___




## Q2

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

# Randomized inputs
shares_outstanding <- round(rnorm(1, mean = 50, sd = 2))
market_cap <- round(rnorm(1, mean = 2.25, sd = 0.5))
debt_outstanding <- round(rnorm(1, mean = 756, sd = 1.5))

# Calculations
share_price <- market_cap *1000 / shares_outstanding
new_shares_to_issue <- debt_outstanding / share_price
```

**Q**: Company Y  has `r round(shares_outstanding , 2)` million shares outstanding and a market capitalization of `r round(market_cap, 2)` billion. It also has `r round(debt_outstanding, 2)` million in debt outstanding. The company  has decided to delever the firm by issuing new equity and completely repaying all the outstanding debt. Assume perfect capital markets. How many new shares must the company issue (in millions)? `r fitb(round(new_shares_to_issue, 2), tol = 1)`

**Answer**: `r round(new_shares_to_issue , 2)` million shares



___


## Q2

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
shares_without <- round(rnorm(1, mean = 2, sd = 1), 2)
price_per_share_without <- round(rnorm(1, mean = 24, sd = 1), 2)
shares_with <- round(rnorm(1, mean = 2, sd = 0.5))
debt_with <- round(rnorm(1, mean = 12, sd = 5))
interest_rate <- 0.05

# MM Proposition I: total firm value is the same
value_without <- shares_without * price_per_share_without
equity_value_with <- value_without - debt_with
price_per_share_with <- equity_value_with / shares_with

```

**Q**: Consider two firms, Leverage and NonLeverage, that have identical assets generating identical cash flows. NonLeverage is an all-equity firm, with `r shares_without` million shares outstanding that trade at `r price_per_share_without` per share. Leverage has `r shares_with` million  shares outstanding and `r debt_with` million in debt, with an interest rate of 5%.

According to Modigliani–Miller Proposition I (with no taxes), what is the stock price for Leverage (in $)? `r fitb(round(price_per_share_with, 2), tol = 0.1)`

**Answer**: `r round(price_per_share_with, 2)`

___
::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p6num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
:::