---
title: "Part 8 (ch15)  Questions Numeric"
---

::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p7num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p9num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
:::


::: {.callout-note}
### For students

**Last updated: `r format(Sys.time(), '%d/%m/%Y')`  **

**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**

:::
___


## Q1

```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

# Randomized parameters
fcf <- round(rnorm(1, mean = 8, sd = 0.2), 2)  # Free cash flow
g <- 0.03  # Growth rate
cost_of_equity <- round(rnorm(1, mean = 0.13, sd = 0.005), 4)
cost_of_debt <- round(rnorm(1, mean = 0.07, sd = 0.005), 4)
tax_rate <- 0.35

# Debt-to-equity ratio and weights
debt_to_equity <- 0.5
debt_to_value <- debt_to_equity / (1 + debt_to_equity)
equity_to_value <- 1 / (1 + debt_to_equity)

# Pre-tax WACC calculation
pre_tax_wacc <- debt_to_value * cost_of_debt + equity_to_value * cost_of_equity

# Value of the unlevered firm (perpetuity growth model)
value_unlevered <- fcf / (pre_tax_wacc - g)
```

**Q1**: Aurora Technologies expects to generate free cash flow of $`r fcf` million over the next year. The company anticipates that its free cash flow will grow at a constant rate of `r g*100`% annually thereafter. Aurora’s cost of equity is `r round(cost_of_equity*100, 2)`%, and its cost of debt is `r round(cost_of_debt*100, 2)`%. The corporate tax rate is `r tax_rate*100`%.

Assuming that Aurora maintains a debt-to-equity ratio of `r debt_to_equity`, what is the company’s pre-tax weighted average cost of capital (WACC) (in %)?
`r fitb(round(pre_tax_wacc*100, 2), tol = 0.1)`

Answer: `r round(pre_tax_wacc*100, 2)`%


___


## Q2

**Q**: What would be the value of Aurora as an all-equity (unlevered) firm (in million dollars)? `r fitb(round(value_unlevered, 0), tol = 1)`

Answer: `r round(value_unlevered, 0)` million dollars

___


## Q3

**Q**: What is Aurora’s after-tax weighted average cost of capital (WACC) (in %)? `r fitb(round((debt_to_value * cost_of_debt * (1 - tax_rate) + equity_to_value * cost_of_equity)*100, 2), tol = 0.1)`

**Answer**: `r round((debt_to_value * cost_of_debt * (1 - tax_rate) + equity_to_value * cost_of_equity)*100, 2)`%


___



## Q4

*Q*: Using the after-tax WACC you calculated, what is the value of Aurora Technologies as a levered firm (in million dollars)? `r fitb(round(fcf / ((debt_to_value * cost_of_debt * (1 - tax_rate) + equity_to_value * cost_of_equity) - g), 0), tol = 1)`

**Answer**: `r round(fcf / ((debt_to_value * cost_of_debt * (1 - tax_rate) + equity_to_value * cost_of_equity) - g), 0)` million dollars

___

## Q5

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)

# Randomized parameters
pre_tax_wacc <- round(rnorm(1, mean = 14, sd = 0.2), 2) / 100
corporate_tax_rate <- 0.25
pre_tax_cost_of_debt <- round(rnorm(1, mean = 7, sd = 0.2), 2) / 100
debt_to_value <- 0.55
equity_to_value <- 1 - debt_to_value

# Calculation of after-tax WACC
after_tax_wacc <- pre_tax_wacc - (debt_to_value * corporate_tax_rate * pre_tax_cost_of_debt) 

```


**Q**: Assume that A's current pre-tax WACC is `r round(pre_tax_wacc*100, 1)`%, the corporate tax rate is `r corporate_tax_rate*100`%, and the pre-tax cost of debt is `r round(pre_tax_cost_of_debt*100,1)`%. If the company were to issue sufficient debt to achieve a debt-to-value ratio of `r debt_to_value`, what would be the after-tax WACC (in %) (ps. ignore personal taxes)?
`r fitb(round(after_tax_wacc*100, 2), tol = 0.1)`

**Answer**: $After-tax WACC =  \frac{E}{D+E} \times re +  \frac{D}{D+E} \times rd - (\frac{D}{D+E} \times rd \times Tc )$ = `r round(after_tax_wacc*100, 2)`%

___





___
::: {style="display: flex; justify-content: space-between; width: 100%;"}
[Go to previous chapter](p7num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
[Go to next chapter](p9num.qmd){.btn .btn-primary role="button" data-toggle="tool" style="margin-right: 430px;"}
:::