---
format:
  html:
    css: webex.css
    include-after-body: webex.js
    theme: themecustom.scss
    fontsize: 1.3em
---

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
library(webexercises)
iinvest <- round(  0.05 +runif(1,0.001,0.01) , 3)
ishares1 <- 1
ishares2 <- 0.75
ishares3 <- 2
ainvest <- 3
share <- ainvest / ishares3
```

**Q:** You founded your own firm two years ago. Initially, you contributed **`r iinvest` million**  of your money and, in return, received **`r round(ishares1,3)` million** shares of stock. Since then, you have sold an additional **`r round(ishares2,3)` million** shares to angel investors. You are now considering raising even more capital from a venture capitalist. The venture capitalist has agreed to invest **`r round(ainvest,3)` million**  and receive **`r round(ishares3,3)` million** shares. Assuming that this is the venture capitalist’s first investment in your company. 

**What is the post-money valuation, in million? ** `r fitb( round( (ishares1 + ishares2 + ishares3 ) * share ,3) , tol=0.001)`

**Assuming that this is the venture capitalist’s first investment in your company, what percentage of the firm will he or she end up owning?**  `r fitb( round( ishares3 / (ishares1 + ishares2 + ishares3 ) * 100 , 3) , tol=0.001)`

**What percentage will you own?**  `r fitb( round( ishares1 / (ishares1 + ishares2 + ishares3 ) * 100 , 3) , tol=0.001)`

**What is the value of your shares, in million?**  `r fitb( round( ishares1  * share ,3) , tol=0.001)`


___

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

seriesapre <- round( runif(1, 1,5) ,3 )
seriesapost <- round(seriesapre +  runif(1, 1,5),3 )

seriesbpre <- round(seriesapost + runif(1, 10,50),3 )
seriesbpost <- round(seriesbpre +  runif(1, 10,50),3 )

seriescpre <- round(seriesbpost + runif(1, 50,70),3 )
seriescpost <- round(seriescpre +  runif(1, 50,70),3 )



```


::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::


___

**Answers**:


1) `r  round( (ishares1 + ishares2 + ishares3 ) * share ,3) `

2) `r round( ishares3 / (ishares1 + ishares2 + ishares3 ) * 100 , 3) `

3) `r round( ishares1 / (ishares1 + ishares2 + ishares3 ) * 100 , 3) `

4) `r  round( ishares1  * share ,3) `

