---
title: 'Estratégia Financeira/Financial Strategy'
subtitle: ' **Part 2 - ch.10 Capital Markets and the Pricing of Risk** '
author:
  - name: ' **Henrique C. Martins (henrique.martins@fgv.br)** '
    affiliation: '**[FGV/EAESP](https://eaesp.fgv.br/en) **'
date-modified: last-modified
title-block-banner: true
format:
  html:
    css: webex.css
    include-after-body: webex.js
---

```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

```


**In-class problems about *chapter 10 Capital Markets and the Pricing of Risk* by [Berk and Demarzo](https://www.amazon.com.br/Corporate-Finance-Global-Jonathan-Berk/dp/1292304154). **


**Solve these problems in class or soon after.**



::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::




___



### True or False

##### Question 1

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Historically, over long horizons, investments in stocks have outperformed investments in bonds."
q1_choices <- c(answer= "True", "False")
cat(q1,longmcq(q1_choices))
```

##### Question 2

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The expected, or mean, return is the return we expect to earn on average."
q1_choices <- c(answer= "True", "False")
cat(q1,longmcq(q1_choices))
```

##### Question 3

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The realized or total return for an investment is the total of the dividend yield and the capital gain rate."
q1_choices <- c(answer= "True", "False")
cat(q1,longmcq(q1_choices))
```

##### Question 4

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The total risk of a security represents only its systematic risk."
q1_choices <- c("True", answer= "False")
cat(q1,longmcq(q1_choices))
```

##### Question 5

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Because investors can eliminate idiosyncratic risk, they do not require a risk premium for taking it on."
q1_choices <- c(answer= "True", "False")
cat(q1,longmcq(q1_choices))
```

##### Question 6

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The market risk premium is the expected average return of the market portfolio."
q1_choices <- c( "True", answer="False")
cat(q1,longmcq(q1_choices))
```

##### Question 7

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The beta of a security is the sensitivity of the security’s return to the return of the overall market."
q1_choices <- c(answer= "True", "False")
cat(q1,longmcq(q1_choices))
```


##### Question 8

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Which of the following risks of a stock are likely to be firm-specific, diversifiable risks, and which are likely to be systematic risks? Which risks will affect the risk premium that investors will demand? (**More than one alternative might be correct.**)"
q1_choices <- c(answer= "The risk that the founder and CEO retires", "The risk that oil prices rise, increasing production costs", answer= "The risk that a product design is faulty and the product must be recalled", "The risk that the economy slows, reducing demand for the firm’s products.")
cat(q1,longmcq(q1_choices))
```



___

##### Expected Return 

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
p1 <- rnorm(1, mean = 10, sd = 2)
p2 <- rnorm(1, mean = 10, sd = 2)
div <- rnorm(1, mean = 1, sd = 0.1)
```

**Q:** You bought a stock one year ago for `r round(p1,3)` per share and sold it today for `r round(p2,3)`. It paid a `r round(div,3)` per share dividend today.

What was your realized return?

`r fitb( round( (p2-p1+div)/p1 * 100 ,3) , tol=0.001)`

How much of the return came from dividend yield and how much came from capital gain?

- Dividend Yield: `r fitb(round( (div)/p1 * 100 ,3) , tol=0.001)`

- Capital gain: `r fitb(round( (p2-p1)/p1 * 100 ,3) , tol=0.001)`









___



##### Risk

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
x <- rnorm(5, mean = 0.05, sd = 0.15)
```

**Q:** What is the expected return of an asset whose historical returns, in percent, of previous periods are `r round(x,3)`? 

`r fitb( round(mean(x),3) *100 , tol=0.001)`

**Q:** What is the variance of an asset whose historical returns, in percent, of previous periods are `r round(x,3)`? 

`r fitb( round(var(x),3) *100 , tol=0.001)`

**Q:** What is the standard deviation of an asset whose historical returns, in percent, of previous periods are `r round(x,3)`? 

`r fitb( round(sd(x),3) *100 , tol=0.001)`










___


##### Cost of Capital

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
mrp <- rnorm(1, mean = 0.08, sd = 0.01)
rf <- rnorm(1, mean = 0.05, sd = 0.01)
beta <- rnorm(1, mean = 1, sd = 0.2)
```

**Q:** Suppose the market risk premium is `r round(mrp,3)` and the risk-free interest rate is `r round(rf,3)`. Calculate the cost of capital of investing in a project with a beta of `r round(beta,3)`? 

`r fitb( round(rf + beta * mrp ,3) , tol=0.001)`







___

::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::





___

##### Answers 

- `r round( (p2-p1+div)/p1 * 100 ,3)`
- `r round( (div)/p1 * 100 ,3)`
- `r round( (p2-p1)/p1 * 100 ,3)`
- `r round(mean(x),3)*100 `
- `r round(var(x),3) *100`
- `r round(sd(x),3) *100`
- `r round(rf + beta * mrp ,3) *100`


