---
format:
  html:
    css: webex.css
    include-after-body: webex.js
    theme: themecustom.scss
    fontsize: 1.4em
---

```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

```

## Cost of Equity Capital

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
mrp <- rnorm(1, mean = 8, sd = 0.01)
rf <- rnorm(1, mean = 5, sd = 0.01)
beta <- rnorm(1, mean = 1, sd = 0.2)
em <- mrp + rf
```

**Q:** Suppose a security's beta is `r round(beta,3)`. If the risk-free rate is `r round(rf,3)` percent and the market risk premium is `r round(mrp,3)` percent, calculate the security's cost of equity capital? 

`r fitb( round(rf + (beta * mrp) ,3), tol=0.01)`

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
mrp2 <- rnorm(1, mean = 8, sd = 0.01)
rf2 <- rnorm(1, mean = 5, sd = 0.01)
beta2 <- rnorm(1, mean = 1, sd = 0.2)
em2 <- mrp + rf
```

**Q:** Suppose a security's beta is `r round(beta2,3)`. If the risk-free rate is `r round(rf2,3)` percent and the expected return of the market portfolio is `r round(em2,3)` percent, calculate the security's cost of equity capital? 

`r fitb( round(rf2 + beta2 * (em2 - rf2 ) ,3) , tol=0.01)`

___

::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::
___


**Answer**:

1) `r round(rf + (beta * mrp) ,3)`

2) `r round(rf2 + beta2 * (em2 - rf2 ) ,3)`



