---
format:
  html:
    css: webex.css
    include-after-body: webex.js
    theme: themecustom.scss
    fontsize: 1.4em
---

```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

```

## Cost of Debt 

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
rf <- rnorm(1, mean = 6.5, sd = 0.01)
yield <- rnorm(1, mean = 10, sd = 0.01)
mrp <- rnorm(1, mean = 8, sd = 0.01)
loss<- rnorm(1, mean = 7, sd = 0.01)
default <- rnorm(1, mean = 50, sd = 0.01)
beta <- 0.15
```

**Q:** Suppose a company has outstanding bonds with a yield to maturity of `r round(yield,3)` percent, a beta of `r round(beta,3)`, a rating with a probability of default of `r round(default,3)` percent and expected loss rate of `r round(loss,3)` percent. If corresponding risk-free rates were `r round(rf,3)` percent, and the market risk premium was `r round(mrp,3)` percent, estimate the expected return of the company's debt using the CAPM and the default rate method.

CAPM: `r fitb( round(rf + beta * mrp ,3), tol=0.01)`

Expected default method: `r fitb( round(yield - default/100 * loss   ,3), tol=0.01)`

___
::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::
___




**Answer**:

CAPM: `r round(rf + beta * mrp ,3)`

Expected default method: `r round(yield - default/100 * loss   ,3)`





