---
title: 'Estratégia Financeira/Financial Strategy'
subtitle: ' **Part 6 - ch.24 Debt Financing** '
author:
  - name: ' **Henrique C. Martins (henrique.martins@fgv.br)** '
    affiliation: '**[FGV/EAESP](https://eaesp.fgv.br/en) **'
  - name: ' **Rafael B. Palazzi (rafaelpalazzi@gmail.com)** '
    affiliation: '**[FGV/EAESP](https://eaesp.fgv.br/en) **'
date-modified: last-modified
title-block-banner: true
format:
  html:
    css: webex.css
    include-after-body: webex.js
---




```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

```


**In-class problems about *chapter 24 Debt Financing* by [Berk and Demarzo](https://www.amazon.com.br/Corporate-Finance-Global-Jonathan-Berk/dp/1292304154). **


**Solve these problems in class or soon after.**

::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::


## True or False

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Corporate debt is typically considered a risk-free investment."
q1_choices <- c("True", answer= "False")
cat(q1,longmcq(q1_choices))
```


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Sovereign debt is a type of corporate debt."
q1_choices <- c( "True", answer= "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Private placement is a method of raising capital that involves selling securities to the general public."
q1_choices <- c("True",  answer= "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Collateralized Debt Obligations (CDOs) are financial instruments that are typically backed by a diversified pool of assets, such as mortgages and loans."
q1_choices <- c( answer= "True", "False")
cat(q1,longmcq(q1_choices))
```


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:**Bond covenants are legally binding agreements that set specific terms and conditions for bond issuers and bondholders, and they can include restrictions on the issuer's activities."
q1_choices <- c( answer= "True", "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Callable bonds give the issuer the right to redeem the bonds before their maturity date, while non-callable bonds cannot be redeemed by the issuer before maturity."
q1_choices <- c( answer= "True", "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Callable bonds usually offer a lower yield than non-callable bonds, which makes them less attractive to investors."
q1_choices <- c( "True", answer="False")
cat(q1,longmcq(q1_choices))
```


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** In a perfect capital market, a firm's market capitalization would change when it borrows to repurchase shares. "
q1_choices <- c( "True", answer="False")
cat(q1,longmcq(q1_choices))
```


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Syndicated bank loans are typically provided by a single bank to a borrower.  "
q1_choices <- c( "True", answer="False")
cat(q1,longmcq(q1_choices))
```





___


::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::
