---
title: 'Estratégia Financeira/Financial Strategy'
subtitle: ' **Part 4 - ch.12 Estimating the Cost of Capital** '
author:
  - name: ' **Henrique C. Martins (henrique.martins@fgv.br)** '
    affiliation: '**[FGV/EAESP](https://eaesp.fgv.br/en) **'
date-modified: last-modified
title-block-banner: true
format:
  html:
    css: webex.css
    include-after-body: webex.js
---




```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

```


**In-class problems about *chapter 12 Estimating the Cost of Capital* by [Berk and Demarzo](https://www.amazon.com.br/Corporate-Finance-Global-Jonathan-Berk/dp/1292304154). **


**Solve these problems in class or soon after.**



::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::



## True or False

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** To implement the CAPM, we must (a) construct the market portfolio, and determine its expected excess return over the risk-free interest rate, and (b) estimate the stock’s beta, or sensitivity to the market portfolio."
q1_choices <- c(answer= "True", "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The market portfolio is a value-weighted portfolio of all securities traded in the market. According to the CAPM, the market portfolio is efficient."
q1_choices <- c(answer= "True", "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** A value-weighted portfolio isn't an equal-ownership portfolio."
q1_choices <- c( "True", answer= "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Beta corresponds to the slope of the best fitting line in the plot of a security’s excess returns versus the market’s standard deviation."
q1_choices <- c(  "True", answer="False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** If we regress a stock’s excess returns against the market’s excess returns, the intercept is the stock’s beta."
q1_choices <- c( "True", answer="False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Because of default risk, the debt cost of capital, which is its expected return to investors, is less than its yield to maturity, which is its promised return."
q1_choices <- c( answer="True", "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** We can estimate a project’s cost of capital based on the asset or unlevered cost of capital of comparable firms in the same line of business."
q1_choices <- c( answer="True", "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Because cash holdings will reduce a firm’s equity beta, when unlevering betas we can use the firm’s net debt, which is debt plus excess cash."
q1_choices <- c( "True", answer="False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Firm or industry asset betas reflect the market risk of the average project in that firm or industry while individual projects may be more or less sensitive to the overall market."
q1_choices <- c( answer="True", "False")
cat(q1,longmcq(q1_choices))
```









## Cost of Equity Capital


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
mrp <- rnorm(1, mean = 0.08, sd = 0.01)
rf <- rnorm(1, mean = 0.05, sd = 0.01)
beta <- rnorm(1, mean = 1, sd = 0.2)
em <- mrp + rf
```


**Q:** Suppose a security's beta is `r round(beta,3)`. If the risk-free rate is `r round(rf,3)` and the market risk premium is `r round(mrp,3)`, calculate the security's cost of equity capital? 

`r fitb( round(rf + beta * mrp ,3), tol=0.001)`



```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
mrp <- rnorm(1, mean = 0.08, sd = 0.01)
rf <- rnorm(1, mean = 0.05, sd = 0.01)
beta <- rnorm(1, mean = 1, sd = 0.2)
em <- mrp + rf
```

**Q:** Suppose a security's beta is `r round(beta,3)`. If the risk-free rate is `r round(rf,3)` and the expected return of the market portfolio is `r round(em,3)`, calculate the security's cost of equity capital? 

`r fitb( round(rf + beta * (em - rf ) ,3) , tol=0.001)`







## Cost of Debt 

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
rf <- rnorm(1, mean = 0.065, sd = 0.01)
yield <- rnorm(1, mean = 0.10, sd = 0.01)
mrp <- rnorm(1, mean = 0.08, sd = 0.01)
loss<- rnorm(1, mean = 0.07, sd = 0.01)
default <- rnorm(1, mean = 0.50, sd = 0.01)
beta <- 0.15
```


**Q:** Suppose a company has outstanding bonds with a yield to maturity of `r round(yield,3)`, a beta of `r round(beta,3)`, and a rating with a probability of default of `r round(default,3)` and expected loss rate of `r round(loss,3)`. If corresponding risk-free rates were `r round(rf,3)`, and the market risk premium was `r round(mrp,3)`, estimate the expected return of the company's debt using the CAPM and the default rate method.


CAPM: `r fitb( round(rf + beta * mrp ,3), tol=0.001)`

Expected default method: `r fitb( round(yield - default * loss   ,3), tol=0.001)`







___

::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::

