---
title: 'Estratégia Financeira/Financial Strategy'
subtitle: ' **Part 5 - ch.13 Investor Behavior and Capital Market Efficiency** '
author:
  - name: ' **Henrique C. Martins (henrique.martins@fgv.br)** '
    affiliation: '**[FGV/EAESP](https://eaesp.fgv.br/en) **'
date-modified: last-modified
title-block-banner: true
format:
  html:
    css: webex.css
    include-after-body: webex.js
---




```{r, setup}
#| eval: true
#| results: asis
#| echo: false
#| warning: false

library(webexercises)

```


**In-class problems about *chapter 13 Investor Behavior and Capital Market Efficiency* by [Berk and Demarzo](https://www.amazon.com.br/Corporate-Finance-Global-Jonathan-Berk/dp/1292304154). **


**Solve these problems in class or soon after.**



::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::



## True or False

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Competition among savvy investors who try to “beat the market” and earn a positive alpha should keep the market portfolio close to efficient much of the time."
q1_choices <- c(answer= "True", "False")
cat(q1,longmcq(q1_choices))
```


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The difference between a stock’s expected return and its required return according to the capital market line is the stock’s alpha."
q1_choices <- c( "True", answer= "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Because beating the market requires enough trading skill to overcome transaction costs as well as behavioral biases, CAPM wisdom that investors should “hold the market” is probably the best advice for most people."
q1_choices <- c( answer="True", "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** If all investors have homogeneous expectations, which states that all investors have the same information, all investors would be aware that the stock had a positive alpha and none would be willing to sell.."
q1_choices <- c( answer= "True", "False")
cat(q1,longmcq(q1_choices))
```


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** Securities always have zero alphas if the market portfolio that is used is not a good proxy for the true market portfolio."
q1_choices <- c( "True", answer="False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** An important conclusion of the CAPM is that investors should never hold the market portfolio combined with risk-free investments."
q1_choices <- c(  "True", answer="False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** There is evidence that individual investors fail to diversify their portfolios adequately (underdiversification bias) and favor investments in companies they are familiar with (familiarity bias)."
q1_choices <- c( answer="True", "False")
cat(q1,longmcq(q1_choices))
```


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** An alternative reason why investors make similar trading errors is that they are actively trying to follow each other’s behavior. This phenomenon, in which individuals imitate each other’s actions, is referred to as disposition effect."
q1_choices <- c( "True", answer= "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** We call the tendency to hang on to losers and sell winners the herd behavior."
q1_choices <- c( "True", answer= "False")
cat(q1,longmcq(q1_choices))
```


```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The relative wealth concerns bias suggests that investors care most about the performance of their portfolio relative to that of their peers."
q1_choices <- c( answer="True", "False")
cat(q1,longmcq(q1_choices))
```

```{r}
#| eval: true
#| results: asis
#| echo: false
#| warning: false
q1 <- " **Q:** The idea that investors can tailor their risk exposures based on common risk factors has become  known amongst as a smart beta strategy."
q1_choices <- c( answer="True", "False")
cat(q1,longmcq(q1_choices))
```




___


::: {.callout-important}
**Type your answers with "." instead of ","! For numerical answers, use 2 decimal places. For instance, if your answer is 0.12345 or 12.345%, type, "12.34" in the box.**
:::
