---
title: 'Empirical Methods in Finance'
subtitle: 'Part 1'
author: 'Henrique C. Martins'
format:
  revealjs: 
    slide-number: true
    theme: simple
    chalkboard: true
    preview-links: auto
    logo: figs/background8.png
    css: logo.css
    footer: '**[**Henrique C. Martins**] [[henrique.martins@fgv.br](mailto:henrique.martins@fgv.br)][Do not use without permission]**  '
    multiplex: true
    scrollable: true 
title-slide-attributes:
    data-background-color: "#b1cafa"
include-after: |
  <script type="text/javascript">
    Reveal.on('ready', event => {
      if (event.indexh === 0) {
        document.querySelector("div.has-logo > img.slide-logo").style.display = "none";
      }
    });
    Reveal.addEventListener('slidechanged', (event) => {
      if (event.indexh === 0) {
        Reveal.configure({ slideNumber: null });
        document.querySelector("div.has-logo > img.slide-logo").style.display = "none";
      }
      if (event.indexh === 1) { 
        Reveal.configure({ slideNumber: 'c' });
        document.querySelector("div.has-logo > img.slide-logo").style.display = null;
      }
    });
  </script>

---


# Basic Statistics



## Basic stats

The following are simple examples of how to compute basic statistics using R. We will start importing the data. Let's use the free dataset `iris`, available in R.


```{r}
#| warning: false
iris <- iris 
```


First, explore the dataset

```{r}
#| warning: false
str(iris) 
```


We have 5 variables: Sepal.Length, Sepal.Width, Petal.Length, Petal.Width e Species. The first four are numeric while the last is a string with three groups: setosa, versicolor, and virginica. The dataset contains 150 observations


Let's take a look at the first 10 observations in the dataset.

```{r}
#| warning: false
head(iris, 10) 
```


Now, let's take a look at the first 5 observations of each species.


```{r}
#| warning: false
by(iris,iris["Species"],head,n=5)
```







### Mean and Median

Now, let's find the means and the medians of the four numeric variables. The most intuitive way is as follows.
```{r}
#| warning: false
mean(iris$Sepal.Length)
mean(iris$Sepal.Width)
mean(iris$Petal.Length)
mean(iris$Petal.Width)
 
median(iris$Sepal.Length)
median(iris$Sepal.Width)
median(iris$Petal.Length)
median(iris$Petal.Width)
```

But this is the easiest way.
```{r}
#| warning: false
summary(iris)
```


See that in the code above you also have the number of observations of each species. If you wanted to know how many observations you have in the dataset, you could use the following line. This might be important in the future.

```{r}
#| warning: false
length(iris$Species)
```


If you want the same thing by group, do as follows:

```{r}
#| warning: false
by(iris, iris$Species, summary)
```







### Minimum and maximum 

The function `summary`already gives you the mininum and maximum of all variables. But sometimes you need to find only these values. You could use the following lines.


```{r}
#| warning: false
min(iris$Sepal.Length)
max(iris$Sepal.Length)
```
      
You could also find the range of values to find the extreme values of a variable.

```{r}
#| warning: false
range(iris$Sepal.Length)
```



If you need the distance between the extreme values, you can use:

```{r}
#| warning: false
max(iris$Sepal.Length) - min(iris$Sepal.Length)
```












### Standard-deviation and Variance

Finally, you can also compute the Standard-deviation and Variance of one variable as follows.


```{r}
#| warning: false
sd(iris$Sepal.Length)
var(iris$Sepal.Length) 
```
If you want the standard deviaation of all variables:

```{r}
#| warning: false
lapply(iris[, 1:4], sd)
```











## Correlation

The following lines will show you a correlation table. First, you need to create a new dataframe with only the numeric variables. This is an extremely important table to your academic paper.

```{r}
#| warning: false
#| message: false
#| error: false
library(dplyr)
iris_num <- select(iris,-Species)
cor(iris_num)
```







## Frequence table

Here is another important table you might use in your paper: the frequency of observations by group.

```{r}
#| warning: false
table(iris$Species)
```






## T-test

Let's create now a t-test of the difference in means. For that, we will use another dataset: `mtcars`. The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles. You can find the description of the variables [here](https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/mtcars).

You will find that there is one variable that is binary: either the cars are automatic (1) or are manual (0).

When you have binary variables, it is always a good idea to test if the means of the variables are different between the two groups of the binary variable.

This is a big thing and you will use a lot in your academic research. In fact, in many articles, the authors explore and compare two groups. So, be ready to create such an analysis.  


First, import the new dataset. Then, repeat the first steps and inspect this dataset (I will not inspect the dataset here, but you should inspect as a way to practice it). 

```{r}
#| warning: false
mtcars <- mtcars
```


Then, use the binary variable to check if the other variables have similar means. In the following case, I am comparing the average of `mpg` (miles per gas) of an automatic with a manual car.


```{r}
#| warning: false
t.test(mpg ~ am, data=mtcars)
```

We see that the average in the automatic car is around 17.1 while the average of manual cars is 24.3.

These averages are statistically different, since the t-stat is high (-3.76) and p-value is low (0.001).

So, we can learn that automatic cars consume more gas than manual cars.

This type of test will be too important in your article.



