
# Graphs

Here, you will find some examples of graphs.

## Scatterplot

```{r}
#| warning: false
library(ggplot2)
library(ggthemes)
iris <- iris 

ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + 
    geom_point(size =2) +   theme_solarized() + 
        labs(title ="My title",
             subtitle = "My subtitle",
             caption = "An explanation about the graph",
             x = "My title for the x-axis (suggestion: Sepal Length)",
             y = "Sepal Width")
```


The same thing with a different pair of variables, but now I am including the linear relationship between the variables.


```{r}
#| warning: false
ggplot(iris, aes(x=Petal.Length, y=Petal.Width)) + 
    geom_point(size =2) +   theme_solarized() +
   geom_point(aes(color = Species))+
   geom_smooth(method='lm')
```

I could actually include a linear relationship by group. In all cases, we observe a positive relationship between the variables, but the relationship seens stonger in `versicolor`.

```{r}
#| warning: false
ggplot(iris, aes(x=Petal.Length, y=Petal.Width, color = Species)) + 
    geom_point(size =2) +   theme_solarized() +
   geom_point(aes(color = Species))+
   geom_smooth(method='lm')
```


## Boxplot

I could also create boxplots using the `iris` dataset. Notice there is one observation with very low Length in the `virginica` group.

```{r}
#| warning: false
ggplot(iris, aes(Species, Sepal.Length, fill=Species)) + 
  geom_boxplot()+ theme_solarized() + 
  scale_y_continuous(breaks= seq(0,30, by=.5)) 
```

## Density plots

Here is a nice-looking density plot.


```{r}
#| warning: false
 ggplot(iris, aes(x=Petal.Length, colour=Species, fill=Species)) +
  geom_density(alpha=.3) + theme_solarized()
```

