

# Types of dataset



```{r setup}
#| warning: false
#| echo: false
#| fig-align: center
#| message: false

library(ggplot2)
library(dplyr)
library(ggthemes)
```





## Cross-sectional data

Here is an example of a cross-sectional dataset. Notice that you have one observation for each unit only. You might have several variables for each unit. Usually, when you create a plot, you will have two variables, one in each axis.

::: panel-tabset

### Plot
```{r}
library(ggplot2)
library(ggthemes)
mtcars <- mtcars
ggplot(mtcars, aes(hp, mpg, color = am)) +
  geom_point() +  geom_smooth(formula = y ~ x, method = "loess") +   theme_solarized()
```

### Data
```{r}
knitr::kable(head(mtcars,30))
```
:::







## Time-series data

Here is an example of a Time-series dataset. Notice that you have one observation per period. You need to pay attention to the **frequency** when you have time-series. Usually, when you create a plot, you will have the period variable as the x-axis.

```{r}
#| echo: true
#| warning: false
#| message: false
library(GetQuandlData)
library(GetTDData)
api_key <- "kfqxH5NsN8Nhe_U1NADB"
first_date <- '2020-01-01'
last_date <- '2022-01-01'
inf <- get_Quandl_series(id_in =  c('Inflation' = 'BCB/433'),
                               api_key = api_key, 
                               first_date = first_date,
                               last_date = last_date)
```


::: panel-tabset
### Plot
```{r}
library(ggplot2)
library(ggthemes)
ggplot(inf, aes( x = ref_date, y= value)) + geom_line() + labs(title = "Selic")+
   theme(axis.text.x = element_text(color = "grey20", size = 15, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 15, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 15, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 15, angle = 90, hjust = .5, vjust = .5, face = "plain")) +   theme_solarized()
```

### Data
```{r}
knitr::kable(inf)
```
:::









## Pooled cross sections data

A pooled cross section dataset combines more than one cross-sectional dataset collected overtime. For instance, when you have data from two non consecutive years. It is hard to create a graph with this dataset, but you can manage to include more than one year in the same plot. 

More about the dataset [here](http://fmwww.bc.edu/ec-p/data/wooldridge/datasets.list.html)

::: panel-tabset
### Plot
```{r}
library(ggplot2)
library(ggthemes)
library(wooldridge)
data('infmrt')
ggplot(infmrt, aes(pcinc, infmort, color=factor(year), group=factor(year))) +   geom_point() + theme_solarized()  
```
### Data
```{r}
knitr::kable(infmrt)
```
:::









## Panel dataset

When you have a Panel, you have both dimensions: a cross-sectional and a time-series. That is, you have several variables from several units through several years. This is the type of dataset that most finance and accounting research deals with.

::: panel-tabset
### Data
```{r}
library(wooldridge)
data('prison')
knitr::kable(head(prison,50))
```

### Plot
```{r}
library(ggplot2)
library(ggthemes)
ggplot(prison, aes(year, black, color=factor(state))) +    theme_solarized()   +    geom_line()
```
### Plot II
```{r}
library(ggplot2)
library(ggthemes)
mean_st <- prison %>%  group_by( state ) %>%  summarise( mean_unem = mean( unem ) )
ggplot(mean_st, aes(state, mean_unem)) +    theme_solarized()   +    geom_point() 
```

### Plot III
```{r}
library(ggplot2)
library(ggthemes)
mean_year <- prison %>%  group_by( year ) %>%  summarise( mean_unem = mean( unem ) )
ggplot(mean_year, aes(year, mean_unem)) +    theme_solarized()   +    geom_point() 
```
:::








