


# Selection problem

```{r}
#| warning: false
#| echo: false
#| fig-align: center
#| message: false
pop <- 5000
sample <- 50
set.seed(1235)
x <- runif(pop, min=0, max=5000)
y <- x/5 + runif(pop, min=0, max=5000)
df <- data.frame(x,y)
```

Imagine that the population contains  **`r pop`** units, from which you can observe only **`r sample`**. 

You want to run a linear model to understand the relationship between x and Y. 

The "true" beta of this relationship is as follows. By "true" I mean the beta you would get should you observe the population (remember though that you don't).

```{r}
#| warning: false
#| fig-align: center
#| message: false
#| fig-width: 7
#| fig-height: 4
#| collapse: true
summary(lm(df$y ~ df$x))
```

So the "true" beta is `r round(summary(lm(df$y ~ df$x))$coefficients[2,1], 3)`. And the t-stat is `r round(summary(lm(df$y ~ df$x))$coefficients[2,3], 3)` 

Plotting this relationship in a graph, you get:


```{r}
#| warning: false
#| echo: false
#| fig-align: center
#| message: false
#| fig-width: 7
#| fig-height: 4
library(ggplot2)
library(ggthemes)
ggplot(df) +  geom_point( aes(x=x, y=y), color = "lightblue") +
              geom_smooth(data = df, aes(x=x, y=y) , method = lm) + 
              theme_solarized() + 
              labs(title = paste("Beta is" , round(summary(lm(df$y ~ df$x))$coefficients[2,1], 3) , 
                                 ", Beta t-stat is" , round(summary(lm(df$y ~ df$x))$coefficients[2,3], 3) , 
                                 ", R2 is" , round(summary(lm(df$y ~ df$x))$r.squared , 3) ,
                                 ", Sample Size is" , nrow(df)    ) ) 
```
___

If you run a linear model using the sample you can observe, you might get this.

```{r}
#| warning: false
#| echo: false
#| fig-align: center
#| message: false
#| fig-width: 7
#| fig-height: 4
library(dplyr)
set.seed(1235)
random <- sample_n(df, sample)
reg <- lm(random$y ~ random$x)
sum <- summary(reg)
ggplot(df) +  geom_point( aes(x=x, y=y), color = "grey") +
              geom_point( data = random, aes(x=x, y=y) , color = "blue") +
              geom_smooth(data = random, aes(x=x, y=y) , method = lm) + 
              theme_solarized() + 
              labs(title = paste("Beta is" , round(reg$coefficients["random$x"], 3) , 
                                 ", Beta t-stat is" , round(summary(reg)$coefficients[2 , 3]   , 3) , 
                                 ", R2 is" , round(summary(reg)$r.squared , 3) ,
                                 ", Sample Size is" , nrow(random)    ) ) 
```
___


Or maybe this:

```{r}
#| warning: false
#| echo: false
#| fig-align: center
#| message: false
#| fig-width: 7
#| fig-height: 4
set.seed(1242)
random <- sample_n(df, sample)
reg <- lm(random$y ~ random$x)
sum <- summary(reg)
ggplot(df) +  geom_point( aes(x=x, y=y), color = "grey") +
              geom_point( data = random, aes(x=x, y=y) , color = "blue") +
              geom_smooth(data = random, aes(x=x, y=y) , method = lm) + 
              theme_solarized() + 
              labs(title = paste("Beta is" , round(reg$coefficients["random$x"], 3) , 
                                 ", Beta t-stat is" , round(summary(reg)$coefficients[2 , 3]   , 3) , 
                                 ", R2 is" , round(summary(reg)$r.squared , 3) ,
                                 ", Sample Size is" , nrow(random)    ) ) 
```

___


Or maybe this:

```{r}
#| warning: false
#| echo: false
#| fig-align: center
#| message: false
#| fig-width: 7
#| fig-height: 4
set.seed(1243)
random <- sample_n(df, sample)
reg <- lm(random$y ~ random$x)
sum <- summary(reg)
ggplot(df) +  geom_point( aes(x=x, y=y), color = "grey") +
              geom_point( data = random, aes(x=x, y=y) , color = "blue") +
              geom_smooth(data = random, aes(x=x, y=y) , method = lm) + 
              theme_solarized() + 
              labs(title = paste("Beta is" , round(reg$coefficients["random$x"], 3) , 
                                 ", Beta t-stat is" , round(summary(reg)$coefficients[2 , 3]   , 3) , 
                                 ", R2 is" , round(summary(reg)$r.squared , 3) ,
                                 ", Sample Size is" , nrow(random)    ) ) 
```

Or maybe several other estimates.


**So, the takeaway is: always remember that you can only observe a sample of the population. If the sample you observe is biased, you will get biased estimates.**



